Should I Airbnb My Property?

### 2017-01-11 abbReturns_Script.Rmd
fixing save and load issues

before.PT <- list(abb.data=abb.data,
                  daily.data=daily.data,
                  ltr.data=ltr.data,
                  listing.data=listing.data)

save(before.PT, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_beforePT.RData")

@@

after.SP <- list(abb.data=abb.data,
                  daily.data=daily.data,
                  ltr.data=ltr.data,
                  listing.data=listing.data)

>>>>

before.PT <- list(abb.data=abb.data,
                  ltr.data=ltr.data)

save(before.PT, subs, file="C:/Dropbox/Research/airBNB/data/analyzed/abb_beforePT.RData")

@@

after.SP <- list(abb.data=abb.data,
                 ltr.data=ltr.data)

### 2017-01-11 abbReturns_Writeup.Rmd
fixing save and load issues

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  library(chron)
  library(plyr)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  library(Hmisc)
  library(kernlab)
  library(lmtest)

@@

```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=TRUE}

  load(paste0(data.path, '/analyzed/abb_working.RData'))

@@

A critical theme that arises out of the extant literature is that fundamentals of the markets for primary dwellings (owner-occupied and long-term rentals) may differ from those of vacation homes (or, by association, short term rentals). Or, in other words, the factors that influence prices and rents in the two are not equivalent. @cho2003impacts find that the second home market is more sensitive to proximity to environmental amenities than the owner occupied market. In Switzerland, @soguel2008impact test to see if second homes pay a higher premium for ski resort access.  Their results fail to show a statistically significant difference in the impact of ski resorts between markets, but do find that other property characteristics have heterogenous effects between the two.

Though issues of second homes were primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism'' [@fuller2014stop] has re-focused some of the problems of short term rentals on large, urban environments. With this move to urban areas, issues such as nuisance, property rights and regulation have naturally arisen.  As a result, the short-term rental market has garnered significant interest in the public policy and legal sphere as of late. As many second homes are not permitted for or regulated as commercial entities, STRs can have serious effects on neighbors in the way of externalies such as noise and congestion [@frost2006commentary].  While strict regulation is often proposed, doing so may constititute regulatory takings [@jefferson2015can].  Other, rights-based, regulatory approaches have been suggested [@miller2014transferable].  Many of the key legal decisions regarding short term rentals, particulary though Airbnb, are still in progress and much remains to be settled in this area in terms of the regulatory and legal environment in which STRs are allowed to operate.

@@

We do not directly observe properties that are utilized in both a short and long term leasing strategy.  Therefore, comparisons are done based on estimated or imputed revenues.  Most specifically, we will estimate short-term revenue for observations of long-term rentals (LTRs) and long-term revenue for observations of short-term rentals (STRs). A preference for short or long term leasing strategy will be determined based on comparing the observed and estimated revenues.

### Comparison

@@

```{r load_beforePT, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}
  data.path <- 'c:/dropbox/research/airBNB/data/'
  load(paste0(data.path, '/analyzed/abb_beforePT.RData'))
  abb.data <- before.PT$abb.data
  ltr.data <- before.PT$ltr.data
  daily.data <- before.PT$daily.data

@@

  abb.types <- ggplot(abb.data, aes(x=type)) +
    geom_bar(color=str.col, fill=str.col) +
    xlab('') +
    ylab('# of Properties\n') +
    labs(title = "Short Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.types <- ggplot(ltr.data, aes(x=type)) +
    geom_bar(color=ltr.col, fill=ltr.col) +
    xlab('') +
    ylab('# of Properties\n') +
    labs(title = "Long Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  abb.data <- subset(abb.data, type != 'Other')
  ltr.data <- subset(ltr.data, type != 'Other')

@@

  abb.data$listing.type <- as.character(abb.data$listing.type)
  abb.data$listing.type[abb.data$listing.type == 'Entire home/apt'] <- 'Entire home'

@@

  ggplot(abb.data, aes(x=listing.type)) +
    geom_bar(color=abb.col[1], fill=abb.col[1]) +
    xlab('') +
    ylab('# of Properties\n') +
    labs(title = "Short Term Rentals \nby Listing Type\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  abb.room <- abb.data[abb.data$listing.type != 'Entire home', ]
  abb.data <- abb.data[abb.data$listing.type == 'Entire home', ]

@@

  # Long term data
  ltr.data <- ltr.data[!is.na(ltr.data$bedrooms), ]
  ltr.data <- ltr.data[ltr.data$bedrooms <= 10, ]

  # Short term data
  abb.data <- abb.data[!is.na(abb.data$bedrooms), ]
  abb.data <- abb.data[abb.data$bedrooms <= 10, ]

@@

   ltrbed <- ggplot(ltr.data, aes(x=bedrooms)) +
    geom_bar(fill=ltr.col, color=ltr.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:10, breaks=1:10)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bedrooms in Long Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  abbbed <- ggplot(abb.data, aes(x=bedrooms)) +
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=0:10, breaks=0:10)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bedrooms in Short Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  abb.data <- abb.data[abb.data$bedrooms < 5, ]
  ltr.data <- ltr.data[ltr.data$bedrooms < 5, ]

@@

  abba <- which(abb.data$bedrooms > 3 & abb.data$type =='Apartment')
  ltra <- which(ltr.data$bedrooms > 3 & ltr.data$type =='Apartment')

  if(length(abba) > 0) abb.data <- abb.data[-abba, ]
  if(length(ltra) > 0) ltr.data <- ltr.data[-ltra, ]

  # Convert 0 Bed to 1 Bed
  abb.data$bedrooms[abb.data$bedrooms == 0] <- 1

@@

  ltr.data <- ltr.data[!is.na(ltr.data$baths), ]
  abb.data <- abb.data[!is.na(abb.data$baths), ]

@@

  ltbath <- ggplot(ltr.data, aes(x=baths)) +
    geom_bar(fill=ltr.col, color=ltr.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:8, breaks=1:8)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bathrooms in Long Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  stbath <- ggplot(abb.data, aes(x=baths)) +
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bathrooms in Short Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Short term data
  abb.data <- abb.data[abb.data$baths < 4, ]
  abb.data <- abb.data[abb.data$baths > 0, ]

  # Long term data
  ltr.data <- ltr.data[ltr.data$baths < 4, ]

@@

  abb.data$baths <- round(abb.data$baths + .01, 0)

@@

  ltr.data$bedbath <- paste0(ltr.data$bedrooms, '..', ltr.data$baths)
  abb.data$bedbath <- paste0(abb.data$bedrooms, '..', abb.data$baths)

@@

  ltb <- ggplot(ltr.data, aes(x=bedbath)) +
    geom_bar(fill=ltr.col, color=ltr.col) +
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bed/Bath Combo in Long Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
    facet_wrap(~type)

@@

  stb <- ggplot(abb.data, aes(x=bedbath)) +
    geom_bar(fill=str.col, color=str.col) +
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bed/Bath Combo in Short Term Rentals\n") +
    scale_y_continuous(breaks=c(1000, 3000, 5000)) +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
    facet_wrap(~type)

@@

  ltr.data <- ltr.data[ltr.data$bedbath %in% acc.bb, ]
  abb.data <- abb.data[abb.data$bedbath %in% acc.bb, ]

@@

  ltr.data <- ltr.data[!is.na(ltr.data$event.price), ]
  abb.data <- abb.data[!is.na(abb.data$nightly.rate), ]

@@

  abb.data$average.daily.rate <- abb.data$average.daily.rate * exch.rate
  abb.data$nightly.rate <- abb.data$nightly.rate * exch.rate
  abb.data$weekly.rate <- abb.data$weekly.rate * exch.rate
  abb.data$monthly.rate <- abb.data$monthly * exch.rate

@@

  daily.data$price <- daily.data$price * exch.rate

@@

  ltr.plot <- ggplot(ltr.data, aes(x=event.price)) +
    geom_density(fill=ltr.col, alpha=.8) +
    ylab('Frequency') +
    xlab('Weekly Rental') +
    ggtitle('Long Term Rentals') +
    scale_x_continuous(limits=c(0, 1500)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank(),
          plot.title = element_text(hjust = 0.5))

  # Nightly Rate plot
  rate.plot <- ggplot(abb.data, aes(x=nightly.rate)) +
    geom_density(fill=str.col, alpha=.8) +
    ylab('Frequency') +
    xlab('Nightly Rate') +
    ggtitle('Short Term Rentals') +
    scale_x_continuous(limits=c(0, 600)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank(),
          plot.title = element_text(hjust = 0.5))

@@

  ltr.data <- ltr.data[ltr.data$event.price >= 200 &
                         ltr.data$event.price <= 1000, ]

@@

  abb.data <- abb.data[abb.data$nightly.rate >= 50 &
                         abb.data$nightly.rate <= 500, ]

@@

```{r load_afterSP, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}
  data.path <- 'c:/dropbox/research/airBNB/data/'
  load(paste0(data.path, '/analyzed/abb_afterSP.RData'))
  abb.data <- after.SP$abb.data
  ltr.data <- after.SP$ltr.data
  daily.data <- after.SP$daily.data
```

@@

  abb.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
    geom_point(data=abb.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) +
    ggtitle('AirBNB Location\nBy Submarket')

@@

  ltr.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
    geom_point(data=ltr.data, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
               alpha=.1) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
   theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) +
    ggtitle('Long Term Rental Location\nBy Submarket')

@@

  abbtype.map <- ggplot() +
    geom_bar(data=abb.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          plot.title = element_text(hjust = 0.5)) +
    ggtitle('AirBNB Property Type By Submarket')

@@

  ltrtype.map <- ggplot() +
    geom_bar(data=ltr.data, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          plot.title = element_text(hjust = 0.5)) +
    ggtitle('Long Term Property Type By Submarket')

@@

 load(paste0(data.path, '/analyzed/abb_results.RData'))
 a<-1

@@

  abbr <- abb.data[,c('bedbath', 'revenue')]
  abbr$tenure <- 'short-term'
  ltrr <- ltr.data[,c('bedbath', 'revenue')]
  ltrr$tenure <- 'long-term'
  allr <- rbind(abbr, ltrr)

@@

  abbir <- abb.imp[,c('bedbath', 'imp.rent', 'med.rate')]
  abbir$tenure.rate <- 'short-term (observed)'
  abbir$tenure.rent <- 'short-term (imputed)'

  ltrir <- ltr.imp[,c('bedbath', 'event.price', 'imp.rate')]
  ltrir$tenure.rate <- 'long-term (imputed)'
  ltrir$tenure.rent <- 'long-term (observed)'

@@

abb.sum <- summary(imp.data$abb.mod)
ltr.sum <- summary(imp.data$ltr.mod)

@@

A major deficit in this analysis is that the potential rents, rates, days on market and occupancy rates are estimated globally.  As a result, there is the likelihood of significant bias within certain submarkets.  Below, we break down the results by type (apartment vs house), by geographic market (5 submarketd listed above) and by type and submarket.  We show only the summary tables and the quantile heat map plots.  Full results can be found on the ....ENTER SHINY WEBSITE....

@@

* Need to explain this

@@

* Need to explain this.

```{r, results="asis", echo=FALSE, fig.cap='Preference Analysis: By Submarket'}

@@

*Logistic regression to explain what is correlated with short-term preference
*3 Model approach, increasing complexity
*Need to explain log odds, interpretation, etc.

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
#full.table$Str.Model <- gsub(" ", "&nbsp;", full.table$Str.Model, fixed=TRUE)
 x.full <- xtable(full.table)
 align(x.full) <- 'lllll'

@@

>>>>

  library(spdep)
  library(maptools)
  library(gstat)
  library(ggplot2)
  library(geosphere)
  library(ggmap)
  library(xtable)
  library(chron)
  library(plyr)
  library(sp)
  library(rgeos)
  library(reshape2)
  library(stringr)
  library(RColorBrewer)
  library(Hmisc)
  library(kernlab)
  library(lmtest)
  library(ROCR)

@@

<!-- # ```{r load_workspace, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, cache=TRUE} -->
<!-- #  -->
<!-- #   load(paste0(data.path, '/analyzed/abb_working.RData')) -->
<!-- #  -->
<!-- # ``` -->

@@

A critical theme that arises out of the extant literature is that fundamentals of the markets for primary dwellings (owner-occupied and long-term rentals) may differ from those of vacation homes (or, by association, short term rentals). Or, in other words, the factors that influence prices and rents in the two are not equivalent. @cho2003impacts find that the second home market is more sensitive to proximity to environmental amenities than the owner occupied market. In Switzerland, @soguel2008impact test to see if second homes pay a higher premium for ski resort access.  Their results fail to show a statistically significant difference in the impact of ski resorts between markets, but do find that other property characteristics have heterogenous effects between the two.  
Though issues of second homes were primarily treated as a rural phenomenom for decades  [@gallent2007second], a wave of ``new urban tourism'' [@fuller2014stop] has re-focused some of the problems of short term rentals on large, urban environments. With this move to urban areas, issues such as nuisance, property rights and regulation have naturally arisen.  As a result, the short-term rental market has garnered significant interest in the public policy and legal sphere as of late. As many second homes are not permitted for or regulated as commercial entities, STRs can have serious effects on neighbors in the way of externalies such as noise and congestion [@frost2006commentary].  While strict regulation is often proposed, doing so may constititute regulatory takings [@jefferson2015can].  Other, rights-based, regulatory approaches have been suggested [@miller2014transferable].  Many of the key legal decisions regarding short term rentals, particulary though Airbnb, are still in progress and much remains to be settled in this area in terms of the regulatory and legal environment in which STRs are allowed to operate.

@@

We do not directly observe properties that are utilized in both a short and long term leasing strategy.  Therefore, comparisons are done based on estimated or imputed revenues.  Most specifically, we will estimate short-term revenue for observations of long-term rentals (LTRs) and long-term revenue for observations of short-term rentals (STRs). A preference for short or long term leasing strategy will be determined based on comparing the observed and estimated revenues.    
### Comparison

@@

```{r load_beforePT, message=FALSE, warning=FALSE, cache=FALSE, comment=FALSE, echo=FALSE, results='hide'}
  data.path <- 'c:/dropbox/research/airBNB/data/'
  load(paste0(data.path, '/analyzed/abb_beforePT.RData'))
  abb.data1 <- before.PT$abb.data
  ltr.data1 <- before.PT$ltr.data

@@

  abb.types <- ggplot(abb.data1, aes(x=type)) +
    geom_bar(color=str.col, fill=str.col) +
    xlab('') +
    ylab('# of Properties\n') +
    labs(title = "Short Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  ltr.types <- ggplot(ltr.data1, aes(x=type)) +
    geom_bar(color=ltr.col, fill=ltr.col) +
    xlab('') +
    ylab('# of Properties\n') +
    labs(title = "Long Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  abb.data1 <- subset(abb.data1, type != 'Other')
  ltr.data1 <- subset(ltr.data1, type != 'Other')

@@

  abb.data1$listing.type <- as.character(abb.data1$listing.type)
  abb.data1$listing.type[abb.data1$listing.type == 'Entire home/apt'] <- 'Entire home'

@@

  ggplot(abb.data1, aes(x=listing.type)) +
    geom_bar(color=abb.col[1], fill=abb.col[1]) +
    xlab('') +
    ylab('# of Properties\n') +
    labs(title = "Short Term Rentals \nby Listing Type\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  abb.data1 <- abb.data1[abb.data1$listing.type == 'Entire home', ]

@@

  # Long term data
  ltr.data1 <- ltr.data1[!is.na(ltr.data1$bedrooms), ]
  ltr.data1 <- ltr.data1[ltr.data1$bedrooms <= 10, ]

  # Short term data
  abb.data1 <- abb.data1[!is.na(abb.data1$bedrooms), ]
  abb.data1 <- abb.data1[abb.data1$bedrooms <= 10, ]

@@

   ltrbed <- ggplot(ltr.data1, aes(x=bedrooms)) +
    geom_bar(fill=ltr.col, color=ltr.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:10, breaks=1:10)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bedrooms in Long Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  abbbed <- ggplot(abb.data1, aes(x=bedrooms)) +
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=0:10, breaks=0:10)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bedrooms in Short Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  abb.data1 <- abb.data1[abb.data1$bedrooms < 5, ]
  ltr.data1 <- ltr.data1[ltr.data1$bedrooms < 5, ]

@@

  abba <- which(abb.data1$bedrooms > 3 & abb.data1$type =='Apartment')
  ltra <- which(ltr.data1$bedrooms > 3 & ltr.data1$type =='Apartment')

  if(length(abba) > 0) abb.data1 <- abb.data1[-abba, ]
  if(length(ltra) > 0) ltr.data1 <- ltr.data1[-ltra, ]

  # Convert 0 Bed to 1 Bed
  abb.data1$bedrooms[abb.data1$bedrooms == 0] <- 1

@@

  ltr.data1 <- ltr.data1[!is.na(ltr.data1$baths), ]
  abb.data1 <- abb.data1[!is.na(abb.data1$baths), ]

@@

  ltbath <- ggplot(ltr.data1, aes(x=baths)) +
    geom_bar(fill=ltr.col, color=ltr.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=1:8, breaks=1:8)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bathrooms in Long Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  stbath <- ggplot(abb.data1, aes(x=baths)) +
    geom_bar(fill=str.col, color=str.col) +
    facet_wrap(~type) +
    scale_x_continuous(labels=0:8, breaks=0:8)+
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bathrooms in Short Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5))

@@

  # Short term data
  abb.data1 <- abb.data1[abb.data1$baths < 4, ]
  abb.data1 <- abb.data1[abb.data1$baths > 0, ]

  # Long term data
  ltr.data1 <- ltr.data1[ltr.data1$baths < 4, ]

@@

  abb.data1$baths <- round(abb.data1$baths + .01, 0)

@@

  ltr.data1$bedbath <- paste0(ltr.data1$bedrooms, '..', ltr.data1$baths)
  abb.data1$bedbath <- paste0(abb.data1$bedrooms, '..', abb.data1$baths)

@@

  ltb <- ggplot(ltr.data1, aes(x=bedbath)) +
    geom_bar(fill=ltr.col, color=ltr.col) +
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bed/Bath Combo in Long Term Rentals\n") +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
    facet_wrap(~type)

@@

  stb <- ggplot(abb.data1, aes(x=bedbath)) +
    geom_bar(fill=str.col, color=str.col) +
    xlab('') +
    ylab('# of Props\n') +
    labs(title = "Bed/Bath Combo in Short Term Rentals\n") +
    scale_y_continuous(breaks=c(1000, 3000, 5000)) +
    theme(plot.title = element_text(hjust = 0.5)) +
    theme(axis.text.x = element_text(angle = 90, vjust=0.4)) +
    facet_wrap(~type)

@@

  ltr.data1 <- ltr.data1[ltr.data1$bedbath %in% acc.bb, ]
  abb.data1 <- abb.data1[abb.data1$bedbath %in% acc.bb, ]

@@

  ltr.data1 <- ltr.data1[!is.na(ltr.data1$event.price), ]
  abb.data1 <- abb.data1[!is.na(abb.data1$nightly.rate), ]

@@

  abb.data1$average.daily.rate <- abb.data1$average.daily.rate * exch.rate
  abb.data1$nightly.rate <- abb.data1$nightly.rate * exch.rate
  abb.data1$weekly.rate <- abb.data1$weekly.rate * exch.rate
  abb.data1$monthly.rate <- abb.data1$monthly * exch.rate

@@

  #daily.data$price <- daily.data$price * exch.rate

@@

  ltr.plot <- ggplot(ltr.data1, aes(x=event.price)) +
    geom_density(fill=ltr.col, alpha=.8) +
    ylab('Frequency') +
    xlab('Weekly Rental') +
    ggtitle('Long Term Rentals') +
    scale_x_continuous(limits=c(0, 1500)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank(),
          plot.title = element_text(hjust = 0.5))

  # Nightly Rate plot
  rate.plot <- ggplot(abb.data1, aes(x=nightly.rate)) +
    geom_density(fill=str.col, alpha=.8) +
    ylab('Frequency') +
    xlab('Nightly Rate') +
    ggtitle('Short Term Rentals') +
    scale_x_continuous(limits=c(0, 600)) +
    theme(axis.title.y=element_blank(),
          axis.text.y=element_blank(),
          axis.ticks.y=element_blank(),
          plot.title = element_text(hjust = 0.5))

@@

  ltr.data1 <- ltr.data1[ltr.data1$event.price >= 200 &
                         ltr.data1$event.price <= 1000, ]

@@

  abb.data1 <- abb.data1[abb.data1$nightly.rate >= 50 &
                         abb.data1$nightly.rate <= 500, ]

@@

```{r load_afterSP, message=FALSE, warning=FALSE, cache=TRUE, comment=FALSE, echo=FALSE, results='hide'}
  data.path <- 'c:/dropbox/research/airBNB/data/'
  load(paste0(data.path, '/analyzed/abb_afterSP.RData'))
  abb.data2 <- after.SP$abb.data
  ltr.data2 <- after.SP$ltr.data

@@

  abb.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
    geom_point(data=abb.data2, aes(x=longitude, y=latitude, color=sub.mrkt), size=.2,
               alpha=.2) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) +
    ggtitle('AirBNB Location\nBy Submarket')

@@

  ltr.map <- ggplot() +
    geom_polygon(data=subs, aes(x=long, y=lat, group=group), color='gray80', fill='gray90') +
    geom_point(data=ltr.data2, aes(x=longitude, y=latitude, color=sub.mrkt), size=.1,
               alpha=.1) +
    scale_color_manual(values=sm.col) +
    scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
    scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
    xlab('') + ylab('')+
   theme(legend.position = 'bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          panel.background = element_rect(fill = "white"),
          axis.text.x = element_blank(),
          axis.text.y = element_blank(),
          axis.ticks = element_blank(),
          axis.title.x=element_blank(),
          axis.title.y=element_blank(),
          panel.border = element_rect(colour = "black", fill=NA, size=1)) +
    guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1))) +
    ggtitle('Long Term Rental Location\nBy Submarket')

@@

  abbtype.map <- ggplot() +
    geom_bar(data=abb.data2, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          plot.title = element_text(hjust = 0.5)) +
    ggtitle('AirBNB Property Type By Submarket')

@@

  ltrtype.map <- ggplot() +
    geom_bar(data=ltr.data2, aes(x=sub.mrkt, fill=sub.mrkt)) +
    scale_fill_manual(values=sm.col) +
    facet_wrap(~type) +
    ylab('# of Properties\n') + xlab('')+
    theme(legend.position = 'bottom',
          legend.title = element_blank(),
          axis.text.x=element_blank(),
          axis.ticks.x=element_blank(),
          plot.title = element_text(hjust = 0.5)) +
    ggtitle('Long Term Property Type By Submarket')

@@

 load(paste0(data.path, '/analyzed/abb_objs.RData'))

@@

  abbr <- abb.revs[,c('bedbath', 'revenue')]
  abbr$tenure <- 'short-term'
  ltrr <- ltr.revs[,c('bedbath', 'revenue')]
  ltrr$tenure <- 'long-term'
  allr <- rbind(abbr, ltrr)

@@

  abbir <- abb.revs[,c('bedbath', 'imp.rent', 'med.rate')]
  abbir$tenure.rate <- 'short-term (observed)'
  abbir$tenure.rent <- 'short-term (imputed)'

  ltrir <- ltr.revs[,c('bedbath', 'event.price', 'imp.rate')]
  ltrir$tenure.rate <- 'long-term (imputed)'
  ltrir$tenure.rent <- 'long-term (observed)'

@@

@@

A major concern about the above analysis is that the estimated rents, rates, days on market and occupancy rates are estimated globally.  As a result, there is the likelihood of significant bias within certain submarkets.  Below, we break down the results by type (apartment vs house), by geographic market (five geographic submarkets listed above) and by type and submarket.

@@

First, we bifurcate our data into houses and apartments.  We then rerun the entire analysis described above for the house and the apartment markets separately. Table X and Figures X (houses) and Y (apartments) illustrate the metrics for these two sub-markets.  The raw probability data shows that over 33% of apartments are more profitable in short term leasing as opposed to just 22% of houses.  The two figures show the quantile preference plots both in the raw and with the SVM categorization.  As is evident from these plots, the likely of short-term rental being more profitable is much greater in the apartment market than in the house market.  For apartments, a 60th rate and a 60th percentile occupancy rate has a better than 50% chance of being more profitable in a short term leasing strategy than a long term one.  In fact, so long as an apartment is in the top 1/4 of occupancy rates, it is more profitable in a short term strategy at almost any price point.  Houses, on the other hand, need either very high rates or very high occupancies to justify a short-term rental.      
The large differences between the `SVM Area' figures and the Actual and Fitted speaks to two points about the data.  First, the difference between the SVM Area and the Fitted number highlight the fact that even when transforming the axes into quantile, the data are still not uniformly distributed across the 2-dimensional space of the plot.  This means that not all areas of the plot have equal weights in the Fitted value.  Second, the Actual and SVM Area figures deviate because of the binary nature of the SVM process.  For example, in many of the short-term preference in the apartment SVM plot there are some long-term preference data points, but just fewer than 50% of total, whereas in the long-term preference areas on the left hand side of the plot nearly all of the points are long-term preference.  The results of the SVM process are the result of a sort of 'gerrymandering' where a clustering by one faction and a dispersal by another can create a result that is not representative of the underlying base population.  Despite this fact, we feel that the SVM Area values are useful for the owner in our scenario because they provide both a value and visual guide that present the possibilities of being more profitable with a short-term strategy, not just what the current distribution of such properties are.

@@

1. Need to explain this.

```{r, results="asis", echo=FALSE, fig.cap='Preference Analysis: By Submarket'}
 names(sm.results)[[1]] <- 'core'

@@

1. Logistic regression to explain what is correlated with short-term preference
2. 3 Model approach, increasing complexity
3. Need to explain log odds, interpretation, etc.

```{r, results='asis', echo=FALSE, message=FALSE, comment=FALSE}
 x.full <- xtable(full.table)
 align(x.full) <- 'lllll'

@@

<!-- Heat map with other characteristics on axis
